data structure
A data structure in C++ is a way of organizing and storing data so it can be accessed and modified efficiently. Different data structures are designed for different tasks, such as searching, sorting, inserting, or deleting data.

1.Linear Data Structures -
Elements are arranged in a sequential order.
Array
Linked List
Stack
Queue

2.Non-Linear Data Structures -
Elements are arranged hierarchically or as networks.
Tree
Graph
Heap
Trie



Another common classification is:

Primitive Data Structures: Integer, Character, Float, Boolean.

Non-Primitive Data Structures:
Linear: Array, Linked List, Stack, Queue.
Non-Linear: Tree, Graph.

===========================================================
stack in c++
A stack is a linear data structure that follows the LIFO (Last In, First Out) principle. Using an array in C++, you can implement a stack with basic operations:

Push: Insert an element.
Pop: Remove the top element.
Peek/Top: View the top element.
isEmpty: Check if the stack is empty.
isFull: Check if the stack is full.

========================================
queue in c++

A queue is a linear data structure that follows the FIFO (First In, First Out) principle. Using an array in C++, you can implement a queue with these basic operations:

Enqueue: Insert an element at the rear.
Dequeue: Remove an element from the front.
Front: View the front element.
isEmpty: Check if the queue is empty.

===============================================

--------------------------
Stack Predefine Function       : -
--------------------------

 |       Function	           |            Description                                  |               	Time Complexity

 |      push(x)	               |            Insert element at the top	                  |                       O(1)
 |      pop()	               |            Remove the top element	                      |                       O(1)
 |      top()	               |            Access the top element	                      |                       O(1)
 |      empty()	               |            Check whether the stack is empty	          |                       O(1)
 |      size()	               |            Return the number of elements	              |                       O(1)
 |      swap(s2)	           |            Swap two stacks	                              |                       O(1)
 |      " = "	               |            Copy one stack into another	                  |                       O(n)

================================================================================================================================

--------------------------
Queue Predefined Functions    : - 
---------------------------

Queue Operation	                          STL Function	                                               Description
Enqueue	push()	Insert an element at the rear of the queue.
Dequeue	pop()	Remove the front element from the queue.
Peek / Front	front()	View the front element without removing it.
Rear / Back	back()	View the last element without removing it.
IsEmpty	empty()	Check whether the queue is empty.
Size	size()	Return the number of elements in the queue.
Swap	swap()	Exchange the contents of two queues.
Copy Queue	=	Copy one queue into another.
