String Programs (SIMPLE ) for Practice : -

1.	Find length of a string.                                                       DONE
2.	Count vowels in a string.                                                      DONE
3.	Count words in a sentence.                                                     DONE
4.	Reverse a string.                                                              DONE
5.	Count digits, alphabets, and special characters.                               DONE                           
6.	Convert string to uppercase.                                                   DONE
7.	Convert string to lowercase.                                                   DONE
8.	Sort characters of a string.                                                   DONE
9.	Remove all spaces from a string.                                               DONE
10. Replace a word in a string.                                                    DONE
11.	Compare two strings.                                                           DONE
------------------------------------------------------------------------------------------------------------------------
12.	Concatenate two strings. 
13. Find frequency of each character. 
14.	Check palindrone string. 
15.	Check whether two strings are anagrams.                                       

------------------------------------------------------------------------------

Based on string Recursion: -

1. Print a string character by character 
2. Print string in reverse order 
3. Count length of string using recursion
4. Count vowels in a string using recursion                                          DONE
5. Count consonents in a string using recursion 
6. Count spaces in a string using recursion 
7. Count uppercase letters in a string using recursion                               DONE
8. Count lowercase letter in a string using recursion                                DONE
9. Check whether a string pallindrone 

--------------------------------------------------------------

// 2-D array programm for practice : -

1. Input and display a 2d array                                                   DONE
2. Find sum of all array                                                          DONE
3. Find average of all array                                                      DONE
4. Find largest Element                                                           DONE
5. Find smallest Element                                                          DONE
6. Count even and odd numbers                                                     DONE
7. Find row wise sum                                                              DONE
8. Find column wise sum                                                           DONE
9. Print diagonal elements                                                        DONE
10. Find transpose of matrix                                                      DONE

 ------------------------------------------------------------------

Based on vector : - 
EASY LEVEL : -

1. Create a vector and store 10 integers in it .
2. Print all elements of a vector using loop .
3. Find the size of a vector 
4. Find the largest element in a vector .
5. Find the smallest element in a vector .
6. Calculate the sum of all element in a vector .
7. Calculate the average of element in a vector .
8. Count the number of even and odd element in a vector .
9. Search for given element in a vector .
10 Reverse a vector without using any library function . 
11. 


MEDIUM LEVEL : -

11. Insert an element at a specific position in a vector .
12. Delete an element from a specific position in a vector.
13. Sort a vector in ascending order.
14. Sort a vector in descending order.
15. Find the second largest element in a vector .
16. Find the second smallest element in a vector .
17. Remove dublicate elements from a array .
18. Merge two vector into a third vector .
19. Find the frequency of each element .
20. Rotate a vector left by one position .

------------------------------------------------------------------------------------