// Set  A

Sum of first n natural numbers                                                                     DONE
Merge two arrays into a sorted array                                                               DONE
Swap two numbers using function                                                                    DONE
Pattern:                                                                                           DONE                                                                           
1
2 2
3 3 3
4 4 4 4
5 5 5 5 5

 Set  B

Sum of even numbers between elements   ( ARRAY)                                                    DONE
Calculate the sum of digits using function                                                         DONE
pattern                                                                                            DONE
1
* *
2 2
* * * *
3 3 3 3 3


// IMP QUES

Swap of two numbers                                                                                DONE                                
Factorial                                                                                          DONE                                                                             
Calculate the sum                                                                                  DONE
Separate even and odd numbers                                                                      DONE
Find the sum of elements at even position and odd position                                         DONE
Calculate the area of a circle                                                                     DONE
Logic for greater number function                                                                  DONE                                                                                       
Check positive or negative number                                                                  DONE                                                                              DONE
One condition logic to check even or odd                                                           DONE                                     
Pass or fail                                                                                       DONE
Leap year program                                                                                  DONE
Calculate simple interest                                                                          DONE
Print numbers from 1 to 100                                                                        DONE
Multiplication table                                                                               DONE
Swap two numbers                                                                                   DONE
Factorial of a number                                                                              DONE
Square and cube of a number                                                                        DONE
Calculate the area of a circle using function                                                      DONE
Reverse a number (array)                                                                           DONE
Largest and smallest element in array                                                              DONE
Sum and average of an array                                                                        DONE
Merge two arrays into one  (ARRAY)                                                                 DONE
Rotate an array                                                                                    DONE
Show any element in array                                                                          DONE                                                                                                                                        
Insert and delete element in array                                                                 DONE
Calculate the sum of digits                                                                        DONE
Separate odd and even numbers into different arrays                                                DONE
Find the sum of odd and even position elements                                                     DONE
Copy one string into another                                                                       DONE
Reverse a string without library function                                                          DONE
Convert uppercase to lowercase and lowercase to uppercase (STRING)                                 DONE
Count vowels and consonants                                                                        DONE
Count number of words in a string                                                                  DONE
Check a string is palindrome or not                                                                DONE
Remove all spaces in a string                                                                      DONE


// MCQ

GCD (Greatest Common Divisor)
Decision making keyword → if
Expression executed in → for loop
Array stored in → contiguous memory
First index of array → 0
Last index of array → size - 1
String length / last function → strlen()
String ends with → \0
Character size → 1 byte
fopen() for open file → if fail → returns NULL
Address operator &
Function with no return value → void
File modes:
Write → w
Read → r
Read and write → r+
*(arr + 2) → arr[2]
String comparison → strcmp()


  




// END SEM QUESTION

## Part A

Q.1 Identify the function used to read input from the user.                               A
(A) scanf()
(B) printf()
(C) input()
(D) get()

Q.2 Select the most suitable data type for storing a whole number.                       C
(A) float
(B) char
(C) int
(D) double

Q.3 Evaluate the output of the expression (5 > 3 && 2 < 1).                              B
(A) 1 (true)
(B) 0 (false)
(C) TRUE
(D) Compiler Error

Q.4 Calculate the result of the integer division 7 / 2.                                 C
(A) 3.5
(B) 2
(C) 3
(D) Compiler Error

Q.5 Trace the output of the loop:


for(int i = 1; i <= 3; i++) {
    printf("%d", i);
}


(A) 123                                                                              A
(B) 12
(C) 1234
(D) Compiler Error

Q.6 The first index of an array in C is:                                           A
(A) 0
(B) 1
(C) -1
(D) Any value

Q.7 Which header is required for string functions in C?                              A
(A) <string.h>
(B) <strings.h>
(C) <str.h>
(D) <cstring>

Q.8 Which operator is used to access the value stored at an address in a pointer?            A
(A) *
(B) &
(C) #
(D) ->

Q.9 Which mode in fopen() is invalid?                                                C
(A) "rb"
(B) "wb"
(C) "bx"
(D) "ab"

Q.10   Dynamic memory in C is allocated using:                                         B
(A) new 
(B) malloc()
(C) dalloc()
(D) create()

---

## Part B

Q.11.1 Apply arithmetic operators to calculate simple interest.
OR
Q.11.2 Construct a loop to print all numbers from 1 to 100. 

Q.12.1 Construct a program to print a right-angled triangle of stars. 
OR
Q.12.2 Apply a program to check if a number is positive, negative, or zero. 

Q.13.1 Develop a program to find the largest between two numbers. **[6 marks]**

Q.14.1 Apply a C program to delete an element from an array at a given position. 
OR
Q.14.2 Apply a C program to check whether a given string is a palindrome without using library functions. 

Q.15.1 Apply a C program to remove all vowels from a given string. 
OR
Q.15.2 Apply a C program to convert a string to uppercase without using built-in functions. 

---

## Part C##

Q.16.1 Apply a C program to concatenate two strings without using strcat().
OR
Q.16.2 Apply a C program using a function to find the factorial of a number. 

Q.17.1 Apply a C program to find the maximum element in an array using a function.
OR
Q.17.2 Apply a C program to count vowels in a string using a user-defined function. 

Q.18.1 Apply a C program to separate odd and even numbers from an array into two arrays. 
OR
Q.18.2 Apply a C program to remove all spaces from a string.

Q.19.1 Apply a C program to find the first non-repeating character in a string. 
OR
Q.19.2 Apply a C program to check whether a number is even or odd using a function. 

Q.20.1 Construct a program to print a counting triangle:
1
2 2
3 3 3
4 4 4 4

OR
Q.20.2 Develop a program to print the multiplication table of a number n. 


