 BASED ON  LOOP , IF-ELSE CONDITION  : -
 
1.  Factorial of a Number if n=5;  fact=5*4*3*2*1=120
2.  Check Prime Number if number is given
3.  Fibonacci Series 0,1,1,2,3,5,8,13
4.  Find the largest digit in a number.   if n=23241   o/p:4
5.  Find the product of digits of a number. if n=231 o/p 2*3*1=6 
6.  Check whether a number is an Armstrong number.
7.  Count Even and Odd Digits:Input a number and count how many even and odd digits it contains.
8.  Find the sum of the first 50 natural numbers.
9.  Print ASCII values of A to Z.
10. Calculate the average of N numbers entered by the user.
11. Armstrong Number Check:Check whether a given number is an Armstrong number.
12. Strong Number Check: Check whether a number is a Strong Number (sum of factorials of digits equals the number).
13. Perfect Number Check: Check whether a number is a Perfect Number.
14. GCD of Two Numbers:Find the Greatest Common Divisor (GCD) using loops.
15. LCM of Two Numbers:Find the Least Common Multiple (LCM) using loops.
16. Decimal to Binary Conversion:Convert a decimal number to binary using loops.
17. Binary to Decimal Conversion:Convert a binary number to decimal using loops.

------------------------------------------------------------------------------------------


TEST 2 : -
1.  Find factorial of a number.
2.  Find power of a number.
3.  Find product of first N natural numbers.
4.  Print string in reverse order using recursion.
5.  Count spaces, uppercase letters, lowercase letters, and digits in a string.
6.  Find the longest substring without repeating characters.
7.  Find the longest substring with at most K distinct characters.
8.  Sort the array using Bubble Sort.   If array = {22, 11, 44, 66, 33}
9 . Search for an element in the given array using Binary Search.
10. Check if two strings are anagrams.
11. Count the frequency of each character in a string.
12. Remove all whitespace from a string.

------------------------------------------------------------------------------------

Linked list : -

1. Create a linked list and display its elements.
2. Insert a node at the beginning of the linked list.
3. Insert a node at the end of the linked list.
4. Insert a node at a specific position in the linked list.
5. Delete a node from the beginning of the linked list.
6. Delete a node from the end of the linked list.
7. Delete a node from a specific position in the linked list.
8. Search for an element in the linked list .









